More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-02-09 2016-Weak-FH-Bisim/WeakBisim.tex
renaming in transitivity

Let $\mathcal{R}''$ be the relation: 
\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
\end{array}
}\,\Pred\land\Pred\,'\}\]

The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
and $s^3$, we take the conjunction of the two predicates. The predicates for different 
values of $s^2$ are collected by a disjunction.

@@

For any $p\in P$ by definition of $\mathcal{R}''$,
$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. We have 
the 
following by definition of bisimulation.
For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
\begin{mathpar}

@@

First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
Indeed for any 
$p$, 
$x$, and 
$y$, $s^2_{px}$
relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
 and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
 More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
 P'}$ 
 is 
 the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
\Pred_{target_{pxy}}\implies 
\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
predicate 
relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).

@@

Additionally, the Post renamings do not modify the predicates that only use non-renamed 
variables, and because of the domain of the renamings:\\
$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
= 
\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land 
\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $

This allows us to conclude: using $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$ 
and the assertions above we obtained the needed property.

>>>>

Let $\mathcal{R}''$ be the relation: 
\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,''\phi)\Big|\begin{array}{l}
\displaystyle\Pred\,''=\bigvee_{ \begin{array}{l}
(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
\end{array}
}\,\Pred\land\Pred\,'\\
\land~ \phi \text{ renames variables of $\mathcal{T}_2$ into fresh variables}
\end{array}\Big\}\]

The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
and $s^3$, we take the conjunction of the two predicates. The predicates for different 
values of $s^2$ are collected by a disjunction. 
Free variables are renamed to avoid further clashes with variables of $\mathcal{T}_2$; in 
practice, because having name clashes between different terms of the disjunction is not 
an issue, there is no need to have a different $\phi$ for each predicate, and we will use 
a global renaming $\phi$ in the following.

@@

For any $p\in P$ by definition of $\mathcal{R}''$,
$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. We have 
the 
following by definition of bisimulation.
For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
Additionally we have $\Pred\,'' = (\bigvee_{p\in P} \Pred_p\land\Pred_p\,')\phi$.
\begin{mathpar}

@@

First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
Indeed for any 
$p$, 
$x$, and 
$y$, $s^2_{px}$
relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
 and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
 More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
 P'}$ 
 is 
 the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
Consequently, for all $p$, $x$, $y$, $(\Pred_{target_{px}}\land 
\Pred_{target_{pxy}})\phi\implies 
\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
predicate 
relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$, note the use 
of the global substitution $\phi$ ensuring that $\Pred\,'_{target_{pxy}}$ does not use 
the variables of $\mathcal{T}_2$).

@@

Additionally, the Post substitutions do not modify the predicates that only use 
non-substituted 
variables, and because of the domain of the substitutions:\\
$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
%
= 
(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
\phi\\
%
\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}\phi}}
\subst{\Post_{OT_{pxy}}}\\
%
= 
\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\subst{\Post_{OT_{px}}\phi}\\
 $
Finally, gathering the previous results:

$\Pred\,'' \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
\Pred_{OT}\land\Pred\,'_p)\phi\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land v\!=\!v_{pxy} \land
\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\subst{\Post_{OT_{px}}\phi}\right)
$

This is the expected property except for the $\subst{\Post_{OT_{px}}\phi}$ however, now, 
this substitution only modifies internal variables of $\Pred\,'_{target_{pxy}}$ that are 
part of no other term of the assertion (in particular neither $\Pred\,''$ nor 
$\Pred_{OT}$), it can thus safely be removed to obtain the needed property.
